Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-19 DGMM2025/paper.tex
Working on intro

    We propose an algorithm that solves the following visibility
    problem: given a digital set $X \subset \Z^d$, two points $p,q$ of
    $X$ are \emph{visible} whenever the Euclidean straight line
    segment $\lbrack p,q \rbrack$ is never at chessboard distance
    ($\infty$-distance) greater or equal to $1$ from $X$. It is
    equivalent to the \emph{cotangency} of $p$ and $q$ in $X$, as
    formalized in \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}, and can
    be viewed as an inclusion problem between sets of lattice points
    in this form. Indeed cells surounding $X$ can be encoded as
    lattice points (Khalimsky coding), as well as the cells covering
    lattice directions. The originality of our method is to encode
    subsets of lattice points as sets of integer intervals and to
    reduce all the inclusion problems as intersections and
    translations of integer intervals.

    We focus on solving efficiently this problem because it is crucial
    in computing geometric normals along digital surfaces that are
    aware of salient features.

>>>>

    We propose an algorithm that solves the following visibility
    problem: given a digital set $X \subset \Z^d$, two points $p,q$ of
    $X$ are \emph{visible} whenever the Euclidean straight line
    segment $\lbrack p,q \rbrack$ is never at chessboard distance
    ($\infty$-distance) greater or equal to $1$ from $X$. It is
    equivalent to the \emph{cotangency} of $p$ and $q$ in $X$, as
    formalized in \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}, and can
    be viewed as an inclusion problem between sets of lattice points
    in this form. Indeed cells surounding $X$ can be encoded as
    lattice points (Khalimsky coding), as well as the cells covering
    lattice directions. The originality of our method is to encode
    subsets of lattice points as sets of integer intervals and to
    reduce all the inclusion problems as intersections and
    translations of integer intervals. For a given lattice vector
    $\mathbf{t}$, we solve the visibility of every pair of points
    $(p,p+\mathbf{t})$ of $X$. Global visibility is achieved by
    testing all sought directions within a given range, and is
    parallelized straightforwardly.

    We focus on solving efficiently this problem because it is crucial
    in computing geometric normals along digital surfaces that are
    aware of salient features. Indeed, 2d discrete tangent estimators
    based on tangency or discrete line segments have proven to be both
    sensitive to sharp corners while multigrid convergent along the
    boundary of digitized smooth shapes
    \cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}.

    or
    normal estimators along digital surfaces have been shown to be
    multigrid convergent on digitization of shapes with smooth
    boundary \cite{Cuel:2014-dgci,Lachaud:2017-lnm}
